\PaperTitle

### 2020-01-19 paper/filter_bubbles.tex
aesthetic
anotehr typo

\subsection{Model}
\par
\noindent \textbf{Users.} We consider a set of users $I$ where each user $i \in I$ faces the same finite set of $N$ items $\mathcal J = \left\{0,1,...,N-1\right\}$. For simplicity, we assume that users only derive pleasure from item $n \in \mathcal{J}$ the first time they consume it.
\par

@@

\frac{3}{4} & \frac{3}{8} & 0.0 \vspace{0.15cm} \\

@@

0.0 &\frac{3}{8} & \frac{3}{4}  \\

@@

Suppose instead that item 0 ends up having a negative valuation so that $y = -0.5 < 0$. Now we have that $\mathbb{E}[x_1] = \mathbb{E}[x_3] = -\frac{1}{4} <  -\frac{1}{8} = \mathbb{E}[x_2] = $ with $\bar{\Sigma}$ remaining the same as when $y = 0.5$. Now, the risk-aversion levels of the user determine the choice in the next period. If the user is risk-neutral ($\gamma = 0$), then she will go across the product space to consume item $2$ in the next period since it has a higher expected value. However, if she is sufficiently risk-averse then she still may consume item $1$ or $3$ since her uncertainty about these items is lower than item $2$. In particular, this will happen when 

>>>>

\subsection{Model}
\par
\xhdr{Users.} We consider a set of users $I$ where each user $i \in I$ faces the same finite set of $N$ items $\mathcal J = \left\{0,1,...,N-1\right\}$. For simplicity, we assume that users only derive pleasure from item $n \in \mathcal{J}$ the first time they consume it.
\par

@@

\frac{3}{4} & \frac{3}{8} & 0 \vspace{0.15cm} \\

@@

0 &\frac{3}{8} & \frac{3}{4}  \\

@@

Suppose instead that item 0 ends up having a negative valuation so that $y = -0.5 < 0$. Now we have that $\mathbb{E}[x_1] = \mathbb{E}[x_3] = -\frac{1}{4} <  -\frac{1}{8} = \mathbb{E}[x_2]$ with $\bar{\Sigma}$ remaining the same as when $y = 0.5$. Now, the risk-aversion levels of the user determine the choice in the next period. If the user is risk-neutral ($\gamma = 0$), then she will go across the product space to consume item $2$ in the next period since it has a higher expected value. However, if she is sufficiently risk-averse then she still may consume item $1$ or $3$ since her uncertainty about these items is lower than item $2$. In particular, this will happen when 
